\bf\mftitle

### 2011-01-13 doc/jInfer/full/architecture/architecture.tex
3154619 Create documentation for jInfer architecture - picture for vektor runner

\jmodule{Initial Grammar Generator} takes an object of type \emph{Input}. This class encapsulates all the input files in 3 collections of \code{File}: \code{documents}, \code{schemas} and \code{queries}. Enumerating these files provides IGG with access to all data it needs to create Initial Grammar.\\

\emph{Simplifier} and \emph{Schema Generator} take grammar, % TODO vektor Link to grammar definition
in other words a list of rules as input. In the first case, this grammar is the Initial Grammar, in the second case it is the simplified grammar.

@@

Each callback interface naturally belongs to the similarly named module interface. As their respective interfaces, also callbacks define one crucial method: \emph{finished}. Each inference module is responsible for invoking this method on the callback it got as a parameter after it has finished its work and has results to be passed on. Again, these 3 finished methods have different arguments based on the inference module.\\

@@

\code{SchemaGeneratorCallback.finished} has two \code{String}s as arguments: \code{schema} is the actual string representation of the resulting schema, \code{extension} is a file extension of the result (such as "dtd" or "xsd") which the framework will use when saving the result in a file.

@@

User running the inference might change his mind and try to stop this. For this reason, modules have to check for this case in every time-consuming place such as long loops with the following code
\begin{verbatim}
  for (forever) {
    if (Thread.interrupted()) {
      throw new InterruptedException();
    }
    doStuff();
  }
\end{verbatim}

@@

% TODO vektor Picture!!!
\begin{enumerate}
	\item Selected IGG's \code{start} is encapsulated with error/interruption handling and executed, passing \code{Input} and first callback as parameters.
	\item When IGG finishes, it invokes callback's \code{finish} method, passing the IG as parameter.
	\item This in turn causes \code{Runner} to encapsulate and execute Simplifier's \code{start}, passing IG from the first callback and the second callback as parameters.
	\item When Simplifier finishes, it invokes callback's \code{finish} method, passing the simplified grammar as parameter.
	\item This again causes \code{Runner} to encapsulate and execute SchemaGen's \code{start}, passing the simplified grammar from the second callback and the third callback as parameters.
	\item SchemaGen finishes and invokes the last callback's \code{finish}, passing the resulting schema and its extension as parameters.
	\item \code{Runner} receives the resulting schema and based on preferences, saves it to a file, displays it, etc.
\end{enumerate}

>>>>

\jmodule{Initial Grammar Generator} takes an object of type \code{Input}. This class encapsulates all the input files in 3 collections of \code{File}: \code{documents}, \code{schemas} and \code{queries}. Enumerating these files provides IGG with access to all data it needs to create Initial Grammar.\\

\jmodule{Simplifier} and \jmodule{Schema Generator} take grammar, % TODO vektor Link to grammar definition
in other words a list of \code{Element}s as input. In the first case, this grammar is the Initial Grammar, in the second case it is the simplified grammar.

@@

Each callback interface naturally belongs to the similarly named module interface. As their respective interfaces, also callbacks define one crucial method: \emph{finished}. Each inference module is responsible for invoking this method on the callback it got as a parameter, after it has finished its work and has results to be passed on. Again, these 3 finished methods have different arguments based on the inference module.\\

@@

\code{SchemaGeneratorCallback.finished()} has two \code{String}s as arguments: \code{schema} is the actual string representation of the resulting schema, \code{extension} is a file extension of the result (such as "dtd" or "xsd") which the framework will use when saving the result in a file.

@@

User running the inference might change his mind and try to stop this. For this reason, modules have to check for this case in every time-consuming place such as long loops with the following code:
\begin{verbatim}
  for (forever) {
    if (Thread.interrupted()) {
      throw new InterruptedException();
    }
    doStuff();
  }
\end{verbatim}

@@

% TODO vektor Picture!!!
\begin{figure}
\centering\includegraphics[scale=\myscale]{runner}
\caption{Runner} \label{runner}
\end{figure}

\begin{enumerate}
	\item Selected IGG's \code{start} is encapsulated with error/interruption handling and executed, passing \code{Input} and first callback as parameters.
	\item When IGG finishes, it invokes callback's \code{finish} method, passing the IG as parameter.
	\item This in turn causes \code{Runner} to encapsulate and execute Simplifier's \code{start}, passing IG from the first callback and the second callback as parameters.
	\item When Simplifier finishes, it invokes callback's \code{finish} method, passing the simplified grammar as parameter.
	\item This again causes \code{Runner} to encapsulate and execute SchemaGen's \code{start}, passing the simplified grammar from the second callback and the third callback as parameters.
	\item SchemaGen finishes and invokes the last callback's \code{finish}, passing the resulting schema and its extension as parameters.
	\item \code{Runner} receives the resulting schema and based on preferences, saves it to a file, displays it, etc.
\end{enumerate}
